Glyph-maps for visualising climate data and models

### 2011-08-25 paper.tex

% Drawing trend lines on map
%   - How to
%   - Comparison to coloring slope
%   - Reference to Grinstein icon plots
% Pickett RM and Grinstein GG (1988). Iconographics 
% displays for visualizing multidimensional data. 
% In Proc. IEEE Conference on Systems, Man, and Cybernetics, pages 514-19.
% Note the later work on metaphoric data display, garbage work!
%   - Alexander Gribov's work http://rosuda.org/software/Gauguin/gauguin.html
%   - Spatial star plots by Andrews http://www.udallas.edu:8080/~andrews/software/software.html
%   - Look at what Bertin does
%
% Interactive graphics
% Data processing
%
% Perhaps the GHCN data? Not gridded
% NOAA data, almost grid, but over ocean, so maps more tricky
% NARCAP from NCAR?
% Fill in with NASA data, to start, try to put new data for final version
\maketitle

@@

@@

@@

>>>>

% Drawing trend lines on map
%   - How to
%   - Comparison to coloring slope
%   - Reference to Grinstein icon plots
% Pickett RM and Grinstein GG (1988). Iconographics 
% displays for visualizing multidimensional data. 
% In Proc. IEEE Conference on Systems, Man, and Cybernetics, pages 514-19.
% Note the later work on metaphoric data display, garbage work!
%   - Alexander Gribov's work http://rosuda.org/software/Gauguin/gauguin.html

%   - Spatial star plots by Andrews http://www.udallas.edu:8080/~andrews/software/software.html
%   - Look at what Bertin does
%
% Interactive graphics
% Data processing
%
% Perhaps the GHCN data? Not gridded
% NOAA data, almost grid, but over ocean, so maps more tricky
% NARCAP from NCAR?
% Fill in with NASA data, to start, try to put new data for final version
\maketitle

@@

\begin{figure*}[htp]
\includegraphics[width=6in]{images/nasa-colored-map.png}
\caption{Facetted map of de-seasonalized temperature.}
\end{figure*}

@@

\begin{figure*}[htp]
\centerline{\includegraphics[width=4in]{images/nasa-deseas-trend.pdf}}
\caption{Time series icon at each location, showing de-seasonalized trend.}
\end{figure*}

\section{Showing seasonal effect, radially oriented icon}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{clouds-heike}%
  \caption{Just as an alternative: shaded map instead of the outlines. }
  \label{fig:cloud-alt}
\end{figure}
